One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-09-21 manuscript/manuscript.tex
abstract

\begin{abstract}
Write this last. About 100 words. 
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%
One-Dimensional Turbulence (ODT) is an accurate and computationally efficient technique for modeling turbulent flows. ODT has been applied to a wide range of flow problems including reaction, multiphase, differential diffusion, heat release, buoyancy, and wall flows. Applications include use as a standalone model and as a closure for Large Eddy Simulation (LES). Its strength lies in the ability to capture a full range of turbulent length and time scales. ODT is somewhat complicated, with a strong coupling between the model formulation and its implementation. We present a modern, open-source, object-oriented C++ implementation of ODT. This code can be used as a starting point to understand, apply, and extend the model, greatly aiding its further use and application in turbulence research.
%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
